Efficient inference using the approximate Riemannian geometry of stochastic population models

### 2012-08-07 paper/paper.tex
Moved to PNAS style file

%\documentclass[useAMS,usenatbib]{biom}
\documentclass[useAMS,usenatbib,referee]{example/biom}

%
%
%  Papers submitted to Biometrics should ALWAYS be prepared
%  using the referee option!!!!

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%

\def\bSig\mathbf{\Sigma}
\newcommand{\VS}{V\&S}
\newcommand{\tr}{\mbox{tr}}

%  If you have a landscape table you need to use the rotating package

\usepackage[figuresright]{rotating}
\graphicspath{{example/}{graphics/}}
%% \raggedbottom % To avoid glue in typesetteing, sbs>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setcounter{footnote}{2}

\title[Efficient inference using the approximate Riemannian geometry of stochastic population models]{Efficient inference using the approximate Riemannian geometry of stochastic population models}

\author{B. Calderhead$^{*}$\email{b.calderhead@ucl.ac.uk} \\
	   Centre for Mathematics and Physics in the Life Sciences and Experimental Biology,\\University College London, UK
	   \and 
	   C. S. Gillespie$^{*}$\email{colin.gillespie@newcastle.ac.uk}\\
	   School of Mathematics \& Statistics, Newcastle University,
	   NE1 7RU, UK
	   }

@@

\date{}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2012}

\volume{XX}
\artmonth{YYYY}
\doi{10.1111/j.1541-0420.2005.00454.x}

%  This label and the label ``lastpage'' are used by the \pagerange
%  command above to give the page range for the article

\label{firstpage}

%  pub the summary here

\begin{abstract}
Abstract
\end{abstract}

%
%  Please place your key words in alphabetical order, separated
%  by semicolons, with the first letter of the first word capitalized,
%  and a period at the end of the list.
%

\begin{keywords}
Stochastic; Moment-closure.
\end{keywords}

\maketitle

@@

\backmatter

%%%%%% include this section if you wish to acknowledge people,
%%%%%% grant support, etc.

\section*{Acknowledgements}

The authors thank Professor A. Sen for some helpful suggestions,
Dr C. R. Rangarajan for a critical reading of the original version of the
paper, and an anonymous referee for very useful comments that improved
the presentation of the paper.\vspace*{-8pt}

%%%%%% include this section only if your manuscript refers to supplementary
%%%%%% materials -- see Instructions for Authors at 
%%%%%% http://www.tibs.org/biometrics

\section*{Supplementary Materials}

Web Appendix 1 referenced in Section~\ref{ss:example} is available
with this paper at the Biometrics website on Wiley Online Library.
\vspace*{-8pt}

\begin{thebibliography}{}
\bibitem[\protect\citeauthoryear{Akash and Tirky}{1988}]{b24} 
Akash, F. J. and Tirky, T. (1988). Proper multivariate conditional
autoregressive models for spatial data analysis. {\it Biometrics} {\bf 196,} 173.

\bibitem[\protect\citeauthoryear{Balaram et~al.}{1985a}]{b2} 
Balaram, C. A., Neeraj, G., Haq, H. J., and Cliff, P. E., (1985a). {\it
NIFT\/} 2nd edition. Boca Raton, Florida: Chapman and Hall.

\bibitem[\protect\citeauthoryear{Commel}{1961}]{b18} 
Commel, J. K. (1961). {\it National Sangget Academia}, 2nd edition.
Hoboken, New Jersey: Wiley.

\bibitem[\protect\citeauthoryear{Das  and Patra}{1986}]{b25} 
Das, B. and Patra, H. M. (1986). Using counts to simultaneously estimate
abundance and detection probabilities in a salamander community. {\it
Herpetologica} {\bf 60,} 468--478.

\bibitem[\protect\citeauthoryear{Emrat}{1974}]{b14} Emrat, T. (1974).
{\it Topics in Stochastic Processes.} New York: Academic  Press.

\bibitem[\protect\citeauthoryear{Emrat}{1985}]{b15} Emrat, T. (1985).
{\it Topics in Stochastic Processes.} New York: Academic  Press.

\bibitem[\protect\citeauthoryear{Goldman et~al.}{1987}]{b9} 
Goldman, M. J. and Ewin, A. (1987). A comparison of smoothing
techniques for CD4 data measured with error in a time-dependent Cox
proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2061--2077.

\bibitem[\protect\citeauthoryear{Goodsman}{1972}]{b8} 
Goodsman, R. C. (1972). Testing hypotheses in the functional linear
model. {\it Scandinavian Journal of Statistics} {\bf 30,} 241--251.

\bibitem[\protect\citeauthoryear{Gooms}{1972}]{b5} Gooms, R. D.
(1972). Goodsman, R.C. (1972). Testing hypotheses in the functional linear
model. {\it Scandinavian Journal of Statistics} {\bf 31,} 315--323.

\bibitem[\protect\citeauthoryear{Gooms  and Wool}{1970}]{b7} Gooms,
R. D. and Wool, N. J. (1970). A comparison of smoothing
techniques for CD4 data measured with errors in a time-dependent Cox
proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2091--2099.

\bibitem[\protect\citeauthoryear{Hackel}{1985}]{b10} 
Hackel, P. (1985). {\it Topics in Stochastic Processes.} New York: Academic  Press.

\bibitem[\protect\citeauthoryear{\nobreak Holloman, \nobreak Tinku,  and Gerg}{Holloman et~al.}{1979}]{b11}
Holloman, P. M., Tinku, H. A., and Gerg, I. (1979). A comparison of smoothing
techniques for CD4 data measured with techniques a time-dependent Cox
proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2105--2111.

\bibitem[\protect\citeauthoryear{Juman}{1986}]{b12} 
Juman, M. (1986). Using counts to simultaneously estimate
abundance and detection probabilities in a salamander community. {\it
Herpetologica} {\bf 61,} 482--495.

\bibitem[\protect\citeauthoryear{Kartik B}{1969}]{b13} 
Kartik, B. V. (1969). Using counts to simultaneously estimate
abundance and detection probabilities in a salamander community. {\it
Herpetologica} {\bf 62,} 511--519.

\bibitem[\protect\citeauthoryear{Lenin}{1932}]{b17} 
Lenin, D. B. (1932). A comparison of smoothing
techniques for CD4 data measured with errors in a time-dependent Cox
proportional hazards model. {\it Statistics in Medicine} {\bf 17,} 2125--2135.

\bibitem[\protect\citeauthoryear{O'Rourke}{1979}]{b4} O'Rourke, D. (1996). Industrial ecology: A 
critical review. {\it International Journal of Environment and Pollution}
{\bf 6,} 389--112.

\bibitem[\protect\citeauthoryear{Oman and \nobreak Raj}{1986}]{b19}
Oman, F. M. and  Raj, E. (1986). {\it Topics in Stochastic Process.} New York: Academic  Press.

\bibitem[\protect\citeauthoryear{Prem et~al.}{1963}]{b20} Prem, G. W., Christ, W., Smap, J.,
Wills, J. A. (1963). {\it Topics in Stochastic Processes.} New York: Academic  Press.

\bibitem[\protect\citeauthoryear{Rahul}{1981}]{b1} Rahul, S. R. (1981).
Industrial ecology: A  critical review. {\it International Journal of
Environment and Pollution} {\bf 6,} 371--375.

\bibitem[\protect\citeauthoryear{Ram  and Shyam}{1972}]{b6} Ram, R. D.
and Shyam, S. (1972). {\it Topics in Stochastic Process.} New York: Academic  Press.

\bibitem[\protect\citeauthoryear{Ravan  and Hari}{1983a}]{b21} Ravan,
M. and Hari, S. (1983). Industrial ecology: A  critical review.
{\it International Journal of Environment and Pollution} {\bf 6,} 389--395.

\bibitem[\protect\citeauthoryear{Ravan  and Hari}{1983b}]{b22}
Ravan, M. and Hari, S. (1984). Industrial ecology: A  critical
review. {\it International Journal of Environment and Pollution} {\bf 7,} 512--519.

\bibitem[\protect\citeauthoryear{Sharma et~al.}{1984}]{b16} Sharma,
F. J. (1984). {\it Topics in Stochastic Process.} New York: Academic Press.

\bibitem[\protect\citeauthoryear{Vim   and Potter}{1988}]{b23} Vim, W.
E. and Potter, H. J. (1988). A  critical
review. {\it International Journal of Environment and Pollution} {\bf 9,} 635--641.

\end{thebibliography}

\label{lastpage}

>>>>

%% PNAStmpl.tex
%% Template file to use for PNAS articles prepared in LaTeX
%% Version: Apr 14, 2008

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% BASIC CLASS FILE 
%% PNAStwo for two column articles is called by default.
%% Uncomment PNASone for single column articles. One column class
%% and style files are available upon request from pnas@nas.edu.
%% (uncomment means get rid of the '%' in front of the command)

%\documentclass{pnasone}
\documentclass{pnastwo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Changing position of text on physical page:
%% Since not all printers position
%% the printed page in the same place on the physical page,
%% you can change the position yourself here, if you need to:

% \advance\voffset -.5in % Minus dimension will raise the printed page on the 
                         %  physical page; positive dimension will lower it.

%% You may set the dimension to the size that you need.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OPTIONAL GRAPHICS STYLE FILE

%% Requires graphics style file (graphicx.sty), used for inserting
%% .eps files into LaTeX articles.
%% Note that inclusion of .eps files is for your reference only;
%% when submitting to PNAS please submit figures separately.

%% Type into the square brackets the name of the driver program 
%% that you are using. If you don't know, try dvips, which is the
%% most common PC driver, or textures for the Mac. These are the options:

% [dvips], [xdvi], [dvipdf], [dvipdfm], [dvipdfmx], [pdftex], [dvipsone],
% [dviwindo], [emtex], [dviwin], [pctexps], [pctexwin], [pctexhp], [pctex32],
% [truetex], [tcidvi], [vtex], [oztex], [textures], [xetex]

%\usepackage[dvips]{graphicx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OPTIONAL POSTSCRIPT FONT FILES

%% PostScript font files: You may need to edit the PNASoneF.sty
%% or PNAStwoF.sty file to make the font names match those on your system. 
%% Alternatively, you can leave the font style file commands commented out
%% and typeset your article using the default Computer Modern 
%% fonts (recommended). If accepted, your article will be typeset
%% at PNAS using PostScript fonts.

% Choose PNASoneF for one column; PNAStwoF for two column:
%\usepackage{PNASoneF}
%\usepackage{PNAStwoF}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ADDITIONAL OPTIONAL STYLE FILES

%% The AMS math files are commonly used to gain access to useful features
%% like extended math fonts and math commands.

\usepackage{amssymb,amsfonts,amsmath}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OPTIONAL MACRO FILES
%% Insert self-defined macros here.
%% \newcommand definitions are recommended; \def definitions are supported

%\newcommand{\mfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2}}
%\def\s{\sigma}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Don't type in anything in the following section:
%%%%%%%%%%%%
%% For PNAS Only:
\contributor{Submitted to Proceedings
of the National Academy of Sciences of the United States of America}
\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}
%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% For titles, only capitalize the first letter
%% \title{Almost sharp fronts for the surface quasi-geostrophic equation}

\title{Efficient inference using the approximate Riemannian geometry of stochastic population models}

%% Enter authors via the \author command.  
%% Use \affil to define affiliations.
%% (Leave no spaces between author name and \affil command)

%% Note that the \thanks{} command has been disabled in favor of
%% a generic, reserved space for PNAS publication footnotes.

%% \author{<author name>
%% \affil{<number>}{<Institution>}} One number for each institution.
%% The same number should be used for authors that
%% are affiliated with the same institution, after the first time
%% only the number is needed, ie, \affil{number}{text}, \affil{number}{}
%% Then, before last author ...
%% \and
%% \author{<author name>
%% \affil{<number>}{}}

%% For example, assuming Garcia and Sonnery are both affiliated with
%% Universidad de Murcia:
%% \author{Roberta Graff\affil{1}{University of Cambridge, Cambridge,
%% United Kingdom},
%% Javier de Ruiz Garcia\affil{2}{Universidad de Murcia, Bioquimica y Biologia
%% Molecular, Murcia, Spain}, \and Franklin Sonnery\affil{2}{}}

\author{B. Calderhead\affil{1}{UCL}, C. S. Gillespie\affil{2}{NCL}}
% \email{b.calderhead@ucl.ac.uk}
% \email{colin.gillespie@newcastle.ac.uk}
% \\
% 	   Centre for Mathematics and Physics in the Life Sciences and Experimental Biology,\\University College London, UK
% 	   \and 
% 	   School of Mathematics \& Statistics, Newcastle University,
% 	   NE1 7RU, UK
\contributor{Submitted to Proceedings of the National Academy of Sciences
of the United States of America}

%% The \maketitle command is necessary to build the title page.
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{article}

\begin{abstract} -- enter abstract text here -- \end{abstract}

%% When adding keywords, separate each term with a straight line: |
\keywords{term | term | term}

%% Optional for entering abbreviations, separate the abbreviation from
%% its definition with a comma, separate each pair with a semicolon:
%% for example:
%% \abbreviations{SAM, self-assembled monolayer; OTS,
%% octadecyltrichlorosilane}

% \abbreviations{}

%% The first letter of the article should be drop cap: \dropcap{}
%\dropcap{I}n this article we study the evolution of ''almost-sharp'' fronts

%% Enter the text of your article beginning here and ending before
%% \begin{acknowledgements}
%% Section head commands for your reference:
%% \section{}
%% \subsection{}
%% \subsubsection{}

@@

%% == end of paper:

%% Optional Materials and Methods Section
%% The Materials and Methods section header will be added automatically.

%% Enter any subheads and the Materials and Methods text below.
%\begin{materials}
% Materials text
%\end{materials}

%% Optional Appendix or Appendices
%% \appendix Appendix text...
%% or, for appendix with title, use square brackets:
%% \appendix[Appendix Title]

\begin{acknowledgments}
Thanks to AG and Ohio state University
\end{acknowledgments}

%% PNAS does not support submission of supporting .tex files such as BibTeX.
%% Instead all references must be included in the article .tex document. 
%% If you currently use BibTeX, your bibliography is formed because the 
%% command \verb+\bibliography{}+ brings the <filename>.bbl file into your
%% .tex document. To conform to PNAS requirements, copy the reference listings
%% from your .bbl file and add them to the article .tex file, using the
%% bibliography environment described above.

%%  Contact pnas@nas.edu if you need assistance with your
%%  bibliography.

% Sample bibliography item in PNAS format:
%% \bibitem{in-text reference} comma-separated author names up to 5,
%% for more than 5 authors use first author last name et al. (year published)
%% article title  {\it Journal Name} volume #: start page-end page.
%% ie,
% \bibitem{Neuhaus} Neuhaus J-M, Sitcher L, Meins F, Jr, Boller T (1991) 
% A short C-terminal sequence is necessary and sufficient for the
% targeting of chitinases to the plant vacuole. 
% {\it Proc Natl Acad Sci USA} 88:10362-10366.

%% Enter the largest bibliography number in the facing curly brackets
%% following \begin{thebibliography}

% \begin{thebibliography}{}
% 
% \end{thebibliography}

\end{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Adding Figure and Table References
%% Be sure to add figures and tables after \end{article}
%% and before \end{document}

%% For figures, put the caption below the illustration.
%%
%% \begin{figure}
%% \caption{Almost Sharp Front}\label{afoto}
%% \end{figure}

%% For Tables, put caption above table
%%
%% Table caption should start with a capital letter, continue with lower case
%% and not have a period at the end
%% Using @{\vrule height ?? depth ?? width0pt} in the tabular preamble will
%% keep that much space between every line in the table.

%% \begin{table}
%% \caption{Repeat length of longer allele by age of onset class}
%% \begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
%% table text
%% \end{tabular}
%% \end{table}

%% For two column figures and tables, use the following:

%% \begin{figure*}
%% \caption{Almost Sharp Front}\label{afoto}
%% \end{figure*}

%% \begin{table*}
%% \caption{Repeat length of longer allele by age of onset class}
%% \begin{tabular}{ccc}
%% table text
%% \end{tabular}
%% \end{table*}
